The KMOS Deep Survey (KDS): dynamical measurements of $z\sim3.5$ main sequence galaxies\thanks{Based on observations obtained at the Very Large Telescope of the European Southern Observatory. Programme IDs: }

### 2017-02-13 paper.tex
finished new draft

% Title of the paper, and the short title which is used in the headers.
% Keep the title short and informative.
\title[KDS: dynamical properties of z$\sim3.5$ galaxies]{The KMOS Deep Survey (KDS): dynamical measurements of $z\sim3.5$ main sequence galaxies\thanks{Based on observations obtained at the Very Large Telescope of the European Southern Observatory. Programme IDs: }}

@@

% Abstract of the paper
\begin{abstract}
We present dynamical measurements of 77 [O~{\sc III}]$\lambda5007$ resolved main sequence star-forming galaxies at $z\sim3.5$ in the mass range $9.5 < log(M_{\star}[M_{\odot}]) < 10.5$ from the KMOS (K-band Multi-Object Spectrograph) Deep Survey (KDS).
These measurements constitute the largest sample at $z > 3$ utilising Integral-Field Spectroscopy (IFS), and provide robust constraints on the internal dynamics, via the intrinsic velocity dispersion $\sigma_{int}$ and rotation velocities, $V_{C}$, of galaxies in the high redshift universe.
We have made careful comparisons to other IFS samples which have been selected consistently, span a wide redshift baseline and use ionised gas emission to trace galaxy dynamics. 
The KDS mean dispersion value is $\sigma_{int} = 70.8^{+3.3}_{-3.1} kms^{-1}$, in agreement with the increase of $\sigma_{int}$ with redshift reported across the comparison samples.
However we find that only $39 \pm 8\%$ of our galaxies are rotationally-dominated ($V_{C}/\sigma_{int}$ > 1), with the sample average $V_{C}/\sigma_{int}$ value much less than at lower redshift.
The rotation dominated KDS galaxies show no clear offset from the local rotation velocity-stellar mass (i.e. $V_{C}-M_{\star}$) relation (the inverse of the stellar mass Tully-Fisher relation), although a smaller fraction of the galaxies sit on the relation due to the increase in the dispersion dominated fraction.
The galaxies show a decrease in specific angular momentum (angular momentum divided by stellar mass) of $\sim0.6-0.7$dex in comparison to $z=0$ disk galaxies, with this evolution the result of the gradual size evolution of the star-forming population over cosmic time.
Due to these more compact sizes, the KDS galaxies show a paucity of virial mass in comparison to stellar mass, which may be explained through an additional virial component originating in random motions, as traced by $\sigma_{int}$.
These observations are in line with a simple equilibrium model picture, in which random motions are boosted in high redshift galaxies by the increase in gas fractions, accretion efficiency, specific star-formation rate and stellar feedback.
\end{abstract}

@@

 \hline
Pointing & RA & DEC & N$_{obs}$ & N$_{Det}$ & $\%$ Det. & N$_{Res}$ & $\%$ Res & N$_{Merg}$ & $\%$ Merg$^{*}$ & Band(s) & Exp. Time (ks) & Seeing ($^{\prime\prime}$)  \\
 \hline
 GOODS-S-P1 & 03:32:22 & -27:52:51 & 20 & 16 & 80 & 12 & 60 & 2 & 17 & K, H & 32.4 & 0.50 \\
GOODS-S-P2 & 03:32:35 & -27:43:15 & 17 & 14 & 82 & 11 & 65 & 2 & 18 & K, H & 31.8 & 0.52 \\
SSA22-FIELD & 22:17:11 & 00:15:47 & 19 & 17 & 89 & 11 & 58 & 2 & 18 & HK & 27.8 & 0.57 \\
SSA22-CLUSTER & 22:17:28 & 00:09:54 & 21 & 15 & 71 & 9 & 46 & 8 & 89 & HK & 38.1 & 0.62 \\
 \hline
\end{tabular}
\begin{tablenotes}
      \small
      \item $^{*}$ Note that the Merger percentage is computed with respect to the number of resolved galaxies; the other percentages are computed with respect to the total number of galaxies observed in that pointing.
    \end{tablenotes}
  \end{threeparttable}
  \end{table*}

@@

\subsection{Morphological Measurements}
For a robust interpretation of the observed velocity fields, it is necessary to separately determine the morphological properties of the galaxies from high-resolution photometry.
This imaging is used primarily to determine morphological parameters which characterise the size (quantified here through the half-light radius, $R_{1/2}$,), morphological position angle, $PA_{morph}$, and axis ratio, $A_{r}$, of the galaxies and helps to distinguish multiple component objects with small angular separations from objects which are morphologically isolated.
In the following sections we describe the approach we have chosen to recover these parameters.
In section \cref{subsubsection:morph_param_summary} we compare the KDS morphological parameters with those described in \cite{VanderWel2012}, and also with spectroscopically confirmed galaxies in different redshift intervals in order to study the size evolution of SFGs across cosmic time.

@@

\noindent
with `r' measured as the distance from the centre of rotation, (xcen, ycen).
This model is then projected onto the cube using the inclination angle determined in \cref{subsubsec:galfitting} and sampled with 4 times higher spatial resolution than the KMOS raw data before binning back to the previous resolution.
The increase in model spatial resolution is necessary to capture the steep velocity gradient across the central region of the rotating galaxy, implied by the use of the arctangent function.
If the model is constructed with equivalent spatial resolution to the data, the rotation curve has a flatter central profile which mimics the effect of beam-smearing.
The velocity decreases with a factor of cos($\phi$) from $PA_{kin}$, where $\phi$ is the angle measured clockwise from $PA_{kin}$, so that $PA_{kin}$ points to the positive side of the velocity field.
In principle then the model has 5 free parameters; $\{(xcen, ycen), PA_{kin}, rt, v_{asym}$, rather than the 6 free parameters in some previous works \citep[e.g.][]{Stott2016}, since we have determined the inclination has been determined from the HST axis ratio.
The intrinsic flux profile of these simulated [O~{\sc III}]$\lambda$5007 lines in the spatial direction is determined using the galfit model derived in section \cref{subsubsec:galfitting} (which assumes that the [O~{\sc III}]$\lambda$5007 emission profile follows the stellar profile), also constructed at 4 times higher spatial resolution than the KMOS cube and rebinned for the same reasons, and the intrinsic velocity dispersion of the line is set to follow a uniform distribution with a default width of 50kms$^{-1}$.
This default line width is selected after examining Figure 10 of \cite{Wisnioski2015}, which shows predictions for the cosmic evolution of velocity dispersion.

@@

Following the construction of a convolved cube and the measurement of the beam-smeared maps we can extract beam-smearing corrected values for $V_{C}$ and $\sigma_{int}$, as described throughout the following subsections.
There have been several different methods used to extract $V_{C}$ and $\sigma_{int}$ in previous surveys at different redshift.
We provide an overview of these surveys in section \cref{subsubsec:comparison_samples} along with the methods used to extract kinematic parameters and the derivation of average values of the parameters used for comparison to the KDS throughout results section \cref{subsec:redshift_evolution}).

\subsubsection{KDS beam-smearing corrected rotation velocities}\label{subsubsec:beam_smearing_corrected_velocities}
We extract $V_{smeared}$ and $V_{C}$ by reading off from the beam-smeared and intrinsic best fitting 2D model grids respectively at $2R_{1/2}$.
The $R_{1/2}$ value used to extract velocities from the KMOS data is found by convolving the intrinsic $R_{1/2}$ value with the PSF of the observations.
The $V_{C}$ value extracted at this radius is a commonly used measure of the `peak' of the rotation curve \citep[e.g.][]{Miller2011,Pelliccia2016,Stott2016,Harrison2017} and is similar also to the $v_{80}$ measurement of the velocity at the radius enclosing 80$\%$ of the total light \citep{Tiley2016a}, and extracting the velocity at $\geqslant 2R_{1/2}$ can be crucial for measuring the majority of the total angular momentum \citep[e.g.]{Obreschkow2015,Harrison2017}.
The beam-smearing correction factor is then given by the ratio $V_{C}/V_{smeared}$, with mean and median values of 1.29 and 1.21 for the KDS galaxies classified as morphologically isolated (see \cref{subsec:morpho-kin-class}).
The distributions of $V_{obs}$ and $V_{C}$ are discussed in more detail in section \cref{subsubsec:observed_and_intrinsic}.
The $V_{C}$ errors are discussed in \cref{appsubsubsec:model_errors}.

@@

\subsubsection{KDS beam-smearing corrected intrinsic dispersions}\label{subsubsec:beam_smearing_corrected_dispersions}
Convolution of the model velocity field with the seeing profile produces a peak in the beam-smeared velocity dispersion map at the centre of rotation.
The model therefore provides a beam-smearing correction for the velocity dispersion in every spaxel, dependent mainly on the magnitude of the velocity gradient, which is equal to the difference between the assumed intrinsic velocity dispersion and the beam-smeared dispersion i.e. $\sigma_{bs} = \sigma_{model} - \sigma_{assumed}$.
This is computed for each spaxel to provide the 2D $\sigma_{bs}$ correction map.
The impact of the value of $\sigma_{assumed}$ on the magnitude of $\sigma_{bs}$ correction is discussed further in section \cref{appsubsubsec:model_errors}.
We note also that not all of the observed $\sigma_{int}$ profiles peak in the centre, and since we do not attempt to fit the velocity dispersions, this is a feature the model cannot reproduce.

@@

To test the robustness of our beam-smearing correction approach we have also computed $V_{C}$ and $\sigma_{int}$ values using the independently derived correction factors, which are a function of the velocity gradient and the ratio $R_{d}/R_{psf}$, detailed in Johnson et al. (in prep), used to evaluate the final kinematic parameters in \cite{Harrison2017}.
These correction factors are applied to $V_{smeared}$ to reach $V_{C}$ and to $\sigma_{obs}$ to reach $\sigma_{int}$.
The $V_{C}$ values agree to within $\sim10\%$, and the $\sigma_{int}$ values to within $\sim5\%$ which is within the errors on these quantities. 
This confirms that the choice of modelling and kinematic parameter extraction described above is consistent with the $z\sim0.9$ KROSS results.

We present the observed and model determined kinematic parameters in table \ref{tab:kin_props} for all of the spatially resolved KDS field galaxies classified as morphologically isolated (29, see section \cref{subsec:morpho-kin-class}).

@@

The dynamical model parameter $PA_{Kin}$ can be compared with $PA_{morph}$ computed by GALFIT in section \cref{subsubsec:galfitting}, to indicate the degree of misalignment between the gaseous and stellar components of the galaxies.
This follows the analysis described in \citep[e.g.][]{Epinat2008,Epinat2012,Barrera-Ballesteros2014,Barrera-Ballesteros2015,Wisnioski2015,Harrison2017} where rotating galaxies generally have $\Delta PA \equiv |PA_{kin}-PA_{morph}| < 20^{\circ}$, with the discrepancy increasing as a function of axis ratio due to $PA_{morph}$ becoming more difficult to measure as the galaxy becomes more `face-on'.
Significant misalignment between the two axes can however be a signature of galaxy interaction.

@@

\subsection{Comparison samples}\label{subsubsec:comparison_samples}
Throughout section \cref{subsec:redshift_evolution} we compare with the results of surveys tracing dynamics with ionised gas emission across a wide redshift baseline, to determine the evolving physical state of SFGs as the age of the universe increases.
The galaxy selection criteria in these surveys, with the exception of \cite{Green2014} as discussed below, consistently pick out main sequence SFGs, and trace the dynamical properties of these by observing either the [O~{\sc III}]$\lambda$5007 or $H\alpha$ ionised gas emission line.
Given the range of modelling and kinematic parameter extraction methods it is important to verify the extent to which the results from these surveys can be directly compared and treated as forming an evolutionary sequence, which we do in the following subsections by considering each survey in turn.
We make use of tabulated data from the surveys deemed directly comparable, where available, to compute sample averages using the following method. 
The fractional error weighted mean of $V_{C}/\sigma_{int}$, $\sigma_{int}$ and $V_{C}$ in each of the samples is computed (i.e. we do not want the derived values with extremely large errors to dominate the averages).
The errors on these mean values are computed in a statistical sense, by generating bootstrapped samples, with replacement, with size equivalent to the original survey sample size and with values perturbed by a random number drawn from a gaussian distribution with width given by the error on the original point.
The same process is applied to compute the errors on the sample medians, and we report the 16th and 84th percentiles of the distributions of each of the above quantities as an indicator of the distribution width, and hence galaxy diversity, at each redshift slice.
These results are listed in table \ref{tab:evolution_numbers} and discussed in detailed throughout section \cref{subsec:redshift_evolution}, where we will make statements about dynamical evolution by connecting the dots of these different surveys, assuming that on average they are tracing a population of SFGs which evolve across cosmic time.

@@

\subsubsection{KMOS$^{3D}$}\label{subsubsec:kmos_3d}
The KMOS$^{3D}$ results described in \cite[W15]{Wisnioski2015} describe KMOS H$\alpha$ observations of $\sim191$ massive SFGs across two redshift slices. 
At $z \sim 1.0$ the galaxies have $log(M_{\star}[M_{\odot}])=10.7$ and at $z \sim 2.3$ the median is $log(M_{\star}[M_{\odot}])=10.9$, approaching an order of magnitude above the KDS median of $log(M_{\star}[M_{\odot}])=10.0$.   The rotational velocity are taken as $V_{C} = \frac{1}{2sin(i)}(v_{obs_{max}} - v_{obs_{min}})$ and $\sigma_{int}$ is extracted from the $\sigma_{obs}$ map far from the kinematic centre, where the effects of beam-smearing are negligible.
No tabulated values are provided, and so we make use of values quoted in W15 at both redshift intervals throughout the section \cref{subsec:redshift_evolution} plots.

\subsubsection{MASSIV}\label{subsubsec:MASSIV}
The MASSIV sample \citep[E12]{Epinat2012} uses SINFONI H$\alpha$ observations of 50 SFGs with median $log(M_{\star}[M_{\odot}])=10.2$ at $z\sim1.2$.
An arctangent function is fit to the data and $V_{C}$ is extracted at $\sim1.7R_{1/2}$ and $\sigma_{int}$ value is derived from the $\sigma_{obs}$ map, by subtracting in quadrature the beam-smearing correction value as per section \cref{subsubsec:beam_smearing_corrected_dispersions}.
We make use of tabulated values presented in E12.

@@

It is unclear whether the $V_{C}$ values for the full sample are directly comparable, but we make use of the tabulated values for completeness, and note that the $V_{C}$ values in C09 are likely biased towards rotation dominated galaxies with a well-settled disk.
We make use of $\sigma_{int}$ values from C09 for comparisons and quote $V_{C}/\sigma_{int}$ and rotation dominated fraction results listed in W15 without distributions in section \cref{subsec:redshift_evolution} plots.

@@

\subsubsection{AMAZE}\label{subsubsec:AMAZE}
The AMAZE sample \cite[G11]{Gnerucci2011} presents SINFONI [O~{\sc III}]$\lambda$5007 measurements for 33 galaxies with median $log(M_{\star}[M_{\odot}])=9.9$ at z $\sim 3$, closest in redshift to the KDS galaxies.
In this study rotation curves and intrinsic velocity dispersions are derived from a modelled exponential mass distribution, with the extracted $V_{C}$ value taken as the large radius limit of the rotation curve and the $\sigma_{int}$ is the maximum of the difference in quadrature between the $\sigma_{obs}$ map and the $\sigma_{model}$ map, which also takes into account instrumental resolution and beam-smearing (see their Eq. 8).
A caveat when comparing with the G11 values is that dynamical properties are computed for 11 rotationally dominated galaxies in their sample, with the remaining 22 galaxies not analysed.
We use tabulated values from G11, however we note that the mean $V_{C}/\sigma_{int}$ values are likely to be biased high when compared with the mean values computed from other surveys which contain a mix of rotation and dispersion dominated galaxies.
Also, for 5 galaxies in G11 $V_{C}$ is not well constrained and no errorbar is given; for these objects we take the fractional error equal to 1.
The $\sigma_{int}$ errors for individual galaxies are generally very small, and for 3 galaxies the $\sigma_{int}$ value is consistent with 0kms$^{-1}$.
For the mean value computations we set these equal to the SINFONI resolution limit of 30kms$^{-1}$.
As a result of these selection caveats we denote G11 results with clear symbols throughout the plots in section \cref{subsec:redshift_evolution} and plot the quoted rotation dominated fraction of 33$\%$ without distribution, noting that this could be higher if any of the 22/33 galaxies not analysed are rotation dominated.

This summary shows that there are many different approaches for computing the same intrinsic kinematic parameters, dictated by data quality and model preference, but, despite this diversity, over the past decade the approaches recently appear to be converging on `modelling out' the effects of beam-smearing using similar approaches.
This trend towards consistency is encouraging, and as described in section \cref{subsec:3d_modelling} we have also shaped our approach towards extracting intrinsic kinematic parameters after correcting for beam-smearing effects quantified in the modelling.
We stress that keeping in mind sample selection, mass ranges and kinematic parameter extraction methods are crucial when comparing results between different surveys.

>>>>

% Title of the paper, and the short title which is used in the headers.
% Keep the title short and informative.
\title[KDS: dynamical properties of 77 z$\sim3.5$ galaxies]{The KMOS Deep Survey (KDS): dynamical measurements of $z\sim3.5$ main sequence galaxies\thanks{Based on observations obtained at the Very Large Telescope of the European Southern Observatory. Programme IDs: }}

@@

% Abstract of the paper
\begin{abstract}
We present dynamical measurements of 77 [O~{\sc III}]$\lambda5007$ resolved main sequence star-forming galaxies at $z\sim3.5$ in the mass range $9.5 < log(M_{\star}[M_{\odot}]) < 10.5$ from the KMOS (K-band Multi-Object Spectrograph) Deep Survey (KDS).
These measurements constitute the largest sample at $z > 3$ utilising Integral-Field Spectroscopy (IFS), and provide robust constraints on the internal dynamics, via the intrinsic velocity dispersion $\sigma_{int}$ and rotation velocities, $V_{C}$, of galaxies in the high redshift universe.
We have made careful comparisons to other IFS samples which have been selected consistently, span a wide redshift baseline and use ionised gas emission to trace galaxy dynamics. 
The KDS mean dispersion value is $\sigma_{int} = 70.8^{+3.3}_{-3.1} kms^{-1}$, in agreement with the increase of $\sigma_{int}$ with redshift reported across the comparison samples.
However we find that only $37 \pm 8\%$ of our galaxies are rotationally-dominated ($V_{C}/\sigma_{int}$ > 1), with the sample average $V_{C}/\sigma_{int}$ value much less than at lower redshift.
The rotation dominated KDS galaxies show no clear offset from the local rotation velocity-stellar mass (i.e. $V_{C}-M_{\star}$) relation (the inverse of the stellar mass Tully-Fisher relation), although a smaller fraction of the galaxies sit on the relation due to the increase in the dispersion dominated fraction.
The galaxies show a decrease in specific angular momentum (angular momentum divided by stellar mass) of $\sim0.6-0.7$dex in comparison to $z=0$ disk galaxies, with this evolution the result of the gradual size evolution of the star-forming population over cosmic time.
Due to these more compact sizes, the KDS galaxies show a paucity of virial mass in comparison to stellar mass, which may be explained through an additional virial component originating in random motions, as traced by $\sigma_{int}$.
These observations are in line with a simple equilibrium model picture, in which random motions are boosted in high redshift galaxies by the increase in gas fractions, accretion efficiency, specific star-formation rate and stellar feedback.
\end{abstract}

@@

 \hline
Pointing & RA & DEC & N$_{obs}$ & N$_{Det}$ & $\%$ Det. & N$_{Res}$ & $\%$ Res & N$_{Merg}$ & $\%$ Merg$^{*}$ & Band(s) & Exp. Time (ks) & Seeing ($^{\prime\prime}$)  \\
 \hline
 GOODS-S-P1 & 03:32:22 & -27:52:51 & 20 & 16 & 80 & 12 & 60 & 2 & 17 & K, H & 32.4 & 0.50 \\
GOODS-S-P2 & 03:32:35 & -27:43:15 & 17 & 14 & 82 & 11 & 65 & 2 & 18 & K, H & 31.8 & 0.52 \\
SSA22-FIELD & 22:17:11 & 00:15:47 & 19 & 17 & 89 & 12 & 63 & 2 & 18 & HK & 27.8 & 0.57 \\
SSA22-CLUSTER & 22:17:28 & 00:09:54 & 21 & 15 & 71 & 9 & 46 & 8 & 89 & HK & 38.1 & 0.62 \\
 \hline
\end{tabular}
\begin{tablenotes}
      \small
      \item $^{*}$ Note that the Merger percentage is computed with respect to the number of resolved galaxies; the other percentages are computed with respect to the total number of galaxies observed in that pointing.
    \end{tablenotes}
  \end{threeparttable}
  \end{table*}

@@

\subsection{Morphological Measurements}
For a robust interpretation of the observed velocity fields, it is necessary to separately determine the morphological properties of the galaxies from high-resolution photometry.
This imaging is used primarily to determine morphological parameters which characterise the size (quantified here through the half-light radius, $R_{1/2}$,), morphological position angle, $PA_{morph}$, and axis ratio, $A_{r}$, of the galaxies and helps to distinguish multiple component objects with small angular separations from objects which are morphologically isolated.
In the following sections we describe the approach we have chosen to recover these parameters.
In \cref{subsubsection:morph_param_summary} we compare the KDS morphological parameters with those described in \cite{VanderWel2012}, and also with spectroscopically confirmed galaxies in different redshift intervals in order to study the size evolution of SFGs across cosmic time.

@@

\noindent
with `r' measured as the distance from the centre of rotation, (xcen, ycen).
This model is then projected onto the cube using the inclination angle determined in \cref{subsubsec:galfitting} and sampled with 4 times higher spatial resolution than the KMOS raw data before binning back to the previous resolution.
The increase in model spatial resolution is necessary to capture the steep velocity gradient across the central region of the rotating galaxy, implied by the use of the arctangent function.
If the model is constructed with equivalent spatial resolution to the data, the rotation curve has a flatter central profile which mimics the effect of beam-smearing.
The velocity decreases with a factor of cos($\phi$) from $PA_{kin}$, where $\phi$ is the angle measured clockwise from $PA_{kin}$, so that $PA_{kin}$ points to the positive side of the velocity field.
In principle then the model has 5 free parameters; $\{(xcen, ycen), PA_{kin}, rt, v_{asym}$, rather than the 6 free parameters in some previous works \citep[e.g.][]{Stott2016}, since we have determined the inclination has been determined from the HST axis ratio.
The intrinsic flux profile of these simulated [O~{\sc III}]$\lambda$5007 lines in the spatial direction is determined using the galfit model derived in \cref{subsubsec:galfitting} (which assumes that the [O~{\sc III}]$\lambda$5007 emission profile follows the stellar profile), also constructed at 4 times higher spatial resolution than the KMOS cube and rebinned for the same reasons, and the intrinsic velocity dispersion of the line is set to follow a uniform distribution with a default width of 50kms$^{-1}$.
This default line width is selected after examining Figure 10 of \cite{Wisnioski2015}, which shows predictions for the cosmic evolution of velocity dispersion.

@@

Following the construction of a convolved cube and the measurement of the beam-smeared maps we can extract beam-smearing corrected values for $V_{C}$ and $\sigma_{int}$, as described throughout the following subsections.
There have been several different methods used to extract $V_{C}$ and $\sigma_{int}$ in previous surveys at different redshift.
We provide an overview of these surveys in \cref{subsubsec:comparison_samples} along with the methods used to extract kinematic parameters and the derivation of average values of the parameters used for comparison to the KDS throughout results \cref{subsec:redshift_evolution}).

\subsubsection{KDS beam-smearing corrected rotation velocities}\label{subsubsec:beam_smearing_corrected_velocities}
We extract $V_{smeared}$ and $V_{C}$ by reading off from the beam-smeared and intrinsic best fitting 2D model grids respectively at $2R_{1/2}$.
The $R_{1/2}$ value used to extract velocities from the KMOS data is found by convolving the intrinsic $R_{1/2}$ value with the PSF of the observations.
The $V_{C}$ value extracted at this radius is a commonly used measure of the `peak' of the rotation curve \citep[e.g.][]{Miller2011,Pelliccia2016,Stott2016,Harrison2017} and is similar also to the $v_{80}$ measurement of the velocity at the radius enclosing 80$\%$ of the total light \citep{Tiley2016a}, and extracting the velocity at $\geqslant 2R_{1/2}$ can be crucial for measuring the majority of the total angular momentum \citep[e.g.]{Obreschkow2015,Harrison2017}.
The beam-smearing correction factor is then given by the ratio $V_{C}/V_{smeared}$, with mean and median values of 1.29 and 1.21 for the KDS galaxies classified as morphologically isolated (see \cref{subsec:morpho-kin-class}).
The distributions of $V_{obs}$ and $V_{C}$ are discussed in more detail in \cref{subsubsec:observed_and_intrinsic}.
The $V_{C}$ errors are discussed in \cref{appsubsubsec:model_errors}.

@@

\subsubsection{KDS beam-smearing corrected intrinsic dispersions}\label{subsubsec:beam_smearing_corrected_dispersions}
Convolution of the model velocity field with the seeing profile produces a peak in the beam-smeared velocity dispersion map at the centre of rotation.
The model therefore provides a beam-smearing correction for the velocity dispersion in every spaxel.
This is dependent primarily on the magnitude of the velocity gradient across the parameter maps, verified by the positive correlation between observed velocities and velocity dispersions.
The 2D beam-smearing correction map, $\sigma_{bs}$, is taken as the difference between the beam-smeared dispersion produced by the model and the assumed intrinsic velocity dispersion i.e. $\sigma_{bs} = \sigma_{model} - \sigma_{assumed}$.

The impact of the value of $\sigma_{assumed}$ on the magnitude of $\sigma_{bs}$ correction is discussed further in \cref{appsubsubsec:model_errors}.
We note also that not all of the observed $\sigma_{int}$ profiles peak in the centre, and since we do not attempt to fit the velocity dispersions, this is a feature the model cannot reproduce.

@@

To test the robustness of our beam-smearing correction approach we have also computed $V_{C}$ and $\sigma_{int}$ values using the independently derived correction factors, which are a function of the velocity gradient and the ratio $R_{d}/R_{psf}$, detailed in Johnson et al. (in prep), used to evaluate the final kinematic parameters in \cite{Harrison2017}.
These correction factors are applied to $V_{smeared}$ to reach $V_{C}$ and to $\sigma_{obs}$ to reach $\sigma_{int}$.
The $V_{C}$ values agree to within $\sim10\%$, and the $\sigma_{int}$ values to within $\sim5\%$ which is within the errors on these quantities. 
This confirms that the choice of modelling and kinematic parameter extraction described above is consistent with the $z\sim0.9$ KROSS results.
We also observe that shape and width of the observed and intrinsic kinematic parameter distributions are equivalent, suggesting that the corrections do not over-extrapolate from the raw numbers.

We present the observed and model determined kinematic parameters in table \ref{tab:kin_props} for all of the spatially resolved KDS field galaxies classified as morphologically isolated (29, see \cref{subsec:morpho-kin-class}).

@@

The dynamical model parameter $PA_{Kin}$ can be compared with $PA_{morph}$ computed by GALFIT in \cref{subsubsec:galfitting}, to indicate the degree of misalignment between the gaseous and stellar components of the galaxies.
This follows the analysis described in \citep[e.g.][]{Epinat2008,Epinat2012,Barrera-Ballesteros2014,Barrera-Ballesteros2015,Wisnioski2015,Harrison2017} where rotating galaxies generally have $\Delta PA \equiv |PA_{kin}-PA_{morph}| < 20^{\circ}$, with the discrepancy increasing as a function of axis ratio due to $PA_{morph}$ becoming more difficult to measure as the galaxy becomes more `face-on'.
Significant misalignment between the two axes can however be a signature of galaxy interaction.

@@

\subsection{Comparison samples}\label{subsubsec:comparison_samples}
Throughout \cref{subsec:redshift_evolution} we compare with the results of surveys tracing dynamics with ionised gas emission across a wide redshift baseline, to determine the evolving physical state of SFGs as the age of the universe increases.
The galaxy selection criteria in these surveys, with the exception of \cite{Green2014} as discussed below, consistently pick out main sequence SFGs, and trace the dynamical properties of these by observing either the [O~{\sc III}]$\lambda$5007 or $H\alpha$ ionised gas emission line.
Given the range of modelling and kinematic parameter extraction methods it is important to verify the extent to which the results from these surveys can be directly compared and treated as forming an evolutionary sequence, which we do in the following subsections by considering each survey in turn.
We make use of tabulated data from the surveys deemed directly comparable, where available, to compute sample averages using the following method. 
The fractional error weighted mean of $V_{C}/\sigma_{int}$, $\sigma_{int}$ and $V_{C}$ in each of the samples is computed (i.e. we do not want the derived values with extremely large errors to dominate the averages).
The errors on these mean values are computed in a statistical sense, by generating bootstrapped samples, with replacement, with size equivalent to the original survey sample size and with values perturbed by a random number drawn from a gaussian distribution with width given by the error on the original point.
The same process is applied to compute the errors on the sample medians, and we report the 16th and 84th percentiles of the distributions of each of the above quantities as an indicator of the distribution width, and hence galaxy diversity, at each redshift slice.
These results are listed in table \ref{tab:evolution_numbers} and discussed in detailed throughout \cref{subsec:redshift_evolution}, where we will make statements about dynamical evolution by connecting the dots of these different surveys, assuming that on average they are tracing a population of SFGs which evolve across cosmic time.

@@

\subsubsection{KMOS$^{3D}$}\label{subsubsec:kmos_3d}
The KMOS$^{3D}$ results described in \cite[W15]{Wisnioski2015} describe KMOS H$\alpha$ observations of $\sim191$ massive SFGs across two redshift slices. 
At $z \sim 1.0$ the galaxies have $log(M_{\star}[M_{\odot}])=10.7$ and at $z \sim 2.3$ the median is $log(M_{\star}[M_{\odot}])=10.9$, approaching an order of magnitude above the KDS median of $log(M_{\star}[M_{\odot}])=10.0$.   The rotational velocity are taken as $V_{C} = \frac{1}{2sin(i)}(v_{obs_{max}} - v_{obs_{min}})$ and $\sigma_{int}$ is extracted from the $\sigma_{obs}$ map far from the kinematic centre, where the effects of beam-smearing are negligible.
No tabulated values are provided, and so we make use of values quoted in W15 at both redshift intervals throughout the \cref{subsec:redshift_evolution} plots.

\subsubsection{MASSIV}\label{subsubsec:MASSIV}
The MASSIV sample \citep[E12]{Epinat2012} uses SINFONI H$\alpha$ observations of 50 SFGs with median $log(M_{\star}[M_{\odot}])=10.2$ at $z\sim1.2$.
An arctangent function is fit to the data and $V_{C}$ is extracted at $\sim1.7R_{1/2}$ and $\sigma_{int}$ value is derived from the $\sigma_{obs}$ map, by subtracting in quadrature the beam-smearing correction value as per \cref{subsubsec:beam_smearing_corrected_dispersions}.
We make use of tabulated values presented in E12.

@@

It is unclear whether the $V_{C}$ values for the full sample are directly comparable, but we make use of the tabulated values for completeness, and note that the $V_{C}$ values in C09 are likely biased towards rotation dominated galaxies with a well-settled disk.
We make use of $\sigma_{int}$ values from C09 for comparisons and quote $V_{C}/\sigma_{int}$ and rotation dominated fraction results listed in W15 without distributions in \cref{subsec:redshift_evolution} plots.

@@

\subsubsection{AMAZE}\label{subsubsec:AMAZE}
The AMAZE sample \cite[G11]{Gnerucci2011} presents SINFONI [O~{\sc III}]$\lambda$5007 measurements for 33 galaxies with median $log(M_{\star}[M_{\odot}])=9.9$ at z $\sim 3$, closest in redshift to the KDS galaxies.
In this study rotation curves and intrinsic velocity dispersions are derived from a modelled exponential mass distribution, with the extracted $V_{C}$ value taken as the large radius limit of the rotation curve and the $\sigma_{int}$ is the maximum of the difference in quadrature between the $\sigma_{obs}$ map and the $\sigma_{model}$ map, which also takes into account instrumental resolution and beam-smearing (see their Eq. 8).
A caveat when comparing with the G11 values is that dynamical properties are computed for 11 rotationally dominated galaxies in their sample, with the remaining 22 galaxies not analysed.
We use tabulated values from G11, however we note that the mean $V_{C}/\sigma_{int}$ values are likely to be biased high when compared with the mean values computed from other surveys which contain a mix of rotation and dispersion dominated galaxies.
Also, for 5 galaxies in G11 $V_{C}$ is not well constrained and no errorbar is given; for these objects we take the fractional error equal to 1.
The $\sigma_{int}$ errors for individual galaxies are generally very small, and for 3 galaxies the $\sigma_{int}$ value is consistent with 0kms$^{-1}$.
For the mean value computations we set these equal to the SINFONI resolution limit of 30kms$^{-1}$.
A total of 6 galaxies either have no errors on $V_{C}$ or have $\sigma_{int}$ values consistent with 0kms$^{-1}$, which we refer to as the AMAZE Unconstrained sample and represent these with clear symbols throughout the plots in \cref{subsec:redshift_evolution}.
This Unconstrained sample also contains the galaxy s\_sa22a-M38 common between the KDS and G11, classified here as a merger due to double HST components and twin peaks in the object spectrum, but classified in G11 as a rotating galaxy with $V_{C} = 346kms^{-1}$ (although the authors discuss the possibility that the galaxy could be either a close pair or two clumps embedded within a rotating disk).
The remaining 5 galaxies we refer to as the AMAZE Clean sample and plot with grey symbols.
We also plot the quoted rotation dominated fraction of 33$\%$ without distribution, noting that this could be higher if any of the 22/33 galaxies not analysed are rotation dominated.

This summary shows that there are many different approaches for computing the same intrinsic kinematic parameters, dictated by data quality and model preference, but, despite this diversity, over the past decade the approaches recently appear to be converging on `modelling out' the effects of beam-smearing using similar approaches.
This trend towards consistency is encouraging, and as described in \cref{subsec:3d_modelling} we have also shaped our approach towards extracting intrinsic kinematic parameters after correcting for beam-smearing effects quantified in the modelling.
We stress that keeping in mind sample selection, mass ranges and kinematic parameter extraction methods are crucial when comparing results between different surveys.

\subsection{Morpho-Kinematic classification}\label{subsec:morpho-kin-class}
We proceed to make use of the morphological and kinematic information described above to classify resolved KDS galaxies into three categories; \textbf{(1)} Rotation Dominated; \textbf{(2)} Dispersion Dominated; \textbf{(3)} Mergers.
Previous studies have used various classification schemes of varying complexity to identify which galaxies fall into these categories, and also to identify galaxy which appear `disky'.
The includes the kinemetry approach which quantifies aysmmetries in the 2D moment maps described in \cite{Shapiro2008} and applied throughout in FS09 and C09.
In \cite{Wisnioski2015} a set of 5 criteria (see their section 4) identify rotationally dominated and disky galaxies in by assessing the smoothness of the velocity gradient, the degree of rotational support through the ratio of the velocity to velocity dispersion, $V_{rot}/\sigma$, the $\Delta PA$misalignment and the position of the kinematic centre in relation to both the peak in the velocity dispersion map and the centroid of the continuum centre (also see \cite{Rodrigues2016} for a re-analysis of KMOS$^{3D}$ data at z$\sim 1$ using the same criteria).   
In \cite{Epinat2012}, a detailed description of a morpho-kinematic classification in outlined throughout their section 4, based on the proximity of counterparts in the imaging, $\Delta PA$ and $V_{C}/\sigma_{int}$.
In \cite{Gnerucci2011} an inclined plane is fit to the velocity map and the $\chi^{2}$ of this fit is evaluated in order to test for the presence of smooth velocity gradients, which they find for the 11/33 galaxies described in \cref{subsubsec:AMAZE}.
